Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-01-06 Manuscript/manuscript.Rmd
updates

Random under-sampling substantially improved classification performance as quantified by F1 and MCC metrics (Figure 14). The increase in performance was present across both overlap count and overlap percent predictor types [??? Again, where is distance?]. Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11). Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal [??? Where is the proof?]. Notably, random under-sampling improved performance when using data at the other resolutions; however, at lower resolutions the performances were lower (Supplementary Figure 15; Supplementary Table 12). These results demonstrate that random under-sampling effectively alleviates class imbalance problem, especially for TAD boundaries detected from high-resolution Hi-C data.

@@

>>>>

When comparing re-sampling techniques it was found that performing 50 iterations of random under-sampling yielded significantly higher results for both F1-Scores and MCC metrics (Figure 6).

Random under-sampling substantially improved classification performance as quantified by F1 and MCC metrics (Figure 14). The increase in performance was present across both overlap count and overlap percent predictor types [??? Again, where is distance?]. Models also featured a decrease in both accuracy and AUC, which was attributed to less inflated false negative rates (Supplementary Table 11).

Variable reduction was found not to have an affect on resampling, and subsequent performances, as any differences were again marginal [??? Where is the proof?]. Notably, random under-sampling improved performance when using data at the other resolutions; however, at lower resolutions the performances were lower (Supplementary Figure 15; Supplementary Table 12). These results demonstrate that random under-sampling effectively alleviates class imbalance problem, especially for TAD boundaries detected from high-resolution Hi-C data.

@@

## Figure 3: Ensemble Framework/Model Building Pipeline

A diagram of the model building pipeline given a combination of inputs from the ensemble framework. The data was split into a 7:3 training set to testing set ratio, an $l_{1}$ norm regularization (LASSO) was implemented, and a random forest classification algorithm was performed. Each model was then validated on the same testing set.

# Figure 4: Class Imbalance

Barplots illustrating the class imbalance problem featured across each of the four different resolutions that were analyzed. Minority classes represent the number of genomic bins that contain a TAD boundary, while the majority classes represent the number of genomic bins that do not contain a TAD boundary.

# Figure 5: Performances of Models with No Class-Balancing

Barplots measuring the predictive performance of models built on imbalanced datasets. The performance metrics considered were accuracy, AUC, F1-Score, and MCC. Performances were compared across 4 resolutions (10 kb, 25kb, 50kb, and 100 kb), for each predictor type (OC, OP, and Distances).
